Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-07-01 paper/paper.tex
Adding conclusions

\subsection{Conclusions}

>>>>

\subsection{Summary and Conclusions}

In recent years, various works have considered the influence of solar wind and geomagnetic control of plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2016}).  The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.

This work presents a comprehensive analysis of two types of events intended to provide insight into the relationship between $\rho_{eq}$ and solar wind and geomagnetic parameters by considering both large geomagnetic events and large $\rho_{eq}$ events.  The major difficulty with this identification is that enhancements in $\rho_{eq}$ can occur for two reasons: (1) extended period of positive $B_z$, which leads to low geomagnetic activity, plasmasphere refilling, and a possible expansion of the plasmasphere to geosynchronous altitudes and (2) strong negative $B_z$, which leads to the inward motion of the higher density plasmasphere and leaves geosynchronous altitudes in the lower density plasma trough just outside of the plasmapause but at the same time magnetospheric processes may be acting to enhance the mass density at geosynchronous altitudes.

On average, around the time of large geomagnetic events, there is a very weak enhancement of $\rho_{eq}$ and this enhancement does not depend on either the interplanetary magnetic field $B_z$ or the intensity of the geomagnetic event.  This indicates that there is an approximate balance between magnetospheric enhancement in $\rho_{eq}$ and any reduction due to the inward motion of the plasmasphere.  $\rho_{eq}$ events are larger when $B_{z}$ is more positive after the onset of the event, which indicates that a substantial portion of the events may due to the apparent mass refilling mechanism described by \cite{Denton2016}.  Without additional information about the location of the plasmapause, it may not be possible to separate out the conditions required for enhancement due to enhanced magnetospheric activity from this mechanism beyond the observation that over a time span of ~10 years, there were ~5 large geomagnetic events that corresponded to large increases in $\rho_{eq}$ at geosynchronous altitudes.
